%% refer q31.tex

\chapter{METHODOLOGY} 

\section{Review from Literature}

We are making a automatic hand sanitizer dispenser with some modification in that we are adding counting system which can count the people we are also adding alert system which can alert the people to sanitize there hands and also we are adding level indicator and refilling system. So we have done some literature surveys for this idea. From refered paper 1 we get idea about Design of Automatic Hand Sanitizer System using arduino From refered paper 2 we get idea about Visitor counter using arduino it is used for accurately counting the number of persons/visitors entering or leaving the premises. if somebody enters the premises then the Counter is incremented by one, or decremented by one if someone leaves the premises. This count will be very accurate.and From refered paper 3 we get idea about Automatic liquid or Water Tank Filling System Controlled Using Arduino in this an automated liquid or water tank filling system is proposed with the help of pump machine we will refill the liquid.

\newpage

\section{Proper Planning}

      We will start our project by making Automatic Sanitizer using Arduino and other components. Then we will create alert system using another sensor and buzzer. It can send alert through alarm to people who try to enter premises without sanitizing. After that we will make counting system for putting at door. It will keep count of how many people have entered the building. Then we will add automatic tank filling system. It helps to refill on its own so sanitizer doesn't require anyone to refill it.

   We referred online courses on Internet of Things. Also referred research paper for getting new ideas. We arranged our group discussion virtually on meet and discuss on how to proceed further. We also collected information for projects by reading different reference books.\par
   As we already know that due to this pandemic, travelling has been restricted, we haven't been able to meet and everything we have discussed is done virtually. So, we have tried to do what we can do in this situation. We have purchased the WIFI module and some more components which we will be requiring in early stage. And also, we are trying to figure out the programming part of the project.

\newpage



 

