%% refer q31.tex

\chapter{INTRODUCTION}

   Demand for hand sanitizer has increased due the coronavirus broke out and spread around the world. Hand sanitizers are usually applied by squirting the sanitizer liquid when one presses a pump with one’s hand .This causes many people to come into contact with the pump handle, which increases the risk of viral transmission. Pressing the pump handle is bothersome, and many pass by without disinfecting their hands. Moreover, each person presses the pump handle differently, making it difficult to predict the amount of use and to manage refills and replacements. For this reason, the actual use of hand sanitizers is reduced, which does not help prevent spread of the virus.
   
   So to avoid the above problem we have to use automatic hand sanitizer dispenser. In this the ultrasonic sensor is used for auto opening the sanitizer and for each opening it will count the number of person who uses the sanitizer. When person enters from the gate then again the IR sensor will count the person. If counting of IR and Ultrasonic sensor are equal then that person is sanitized and if it is not equal then alert message will go to bolt IoT and buzzer will indicate that someone is not used the sanitizer. This process is programmed through arduino. 
    
   The main sanitizer bottle is also connected to secondary bottle whose size is greater than main bottle. The main bottle is connected to a water level indicator which indicates the level of water if it is low then it will indicate and pumps the sanitizer from secondary bottle to main bottle and manages the refills. This process is also programmed through arduino.


\vspace{0.6cm}


  

 


